Bathtub Qualitative Reasoning

### 2016-10-21 paper.tex
log2

In figure \ref{state-graph} shows all possible behaviors of the system described above. Blue nodes are final states, which are states without other reachable states. Other nodes are red and each arrow represents a transition.

\begin{figure}\label{state-graph}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{result.png}
\caption{Plot of the state-graph}
\end{figure}

@@

>>>>

In figure \ref{state-graph-base} shows all possible behaviors of the system described above. Blue nodes are final states, which are states without other reachable states. Other nodes are red and each arrow represents a transition.

\begin{figure}\label{state-graph-base}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{result_base_problem.png}
\caption{Plot of the state-graph of the base problem}
\end{figure}

\section{Trace}

@@

\begin{figure}\label{state-graph-extra}
	\centering
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{result_extra_problem.png}
	\caption{Plot of the state-graph of the extra problem}
\end{figure}
